The Power of Liberty in the American Workplace: Unveiling the Global Impact of Free Will Perceptions on Job Satisfaction

### 2024-02-15 outputs/paper/paper.qmd
added comparative section to results

```{r,include=FALSE,message=FALSE,warning=FALSE}
anova_result <- aov(freewill ~ age_group, data =wvs_data_usa  )
summary(anova_result)
```
Interestingly, there are virtually no differences in the average belief in free will between the different age groups surveyed (@fig-ageboxplotwvs in @sec-appendix). ANOVA confirmed that there are no significant differences (*F*(4,12809) = 1.032, *p* = 0.358).

@@

## Demographic Boxplots for World Values Survey
```{r}
#| echo: false
#| warning: false
#| message: false
#| label: fig-ageboxplotwvs
#| fig-cap: "Belief in Free Will by Age Group in WVS 1981-2022"

>>>>

```{r,include=FALSE,message=FALSE,warning=FALSE}
# inferential statistics age group and freewill
anova_result <- aov(freewill ~ age_group, data =wvs_data_usa  )
summary(anova_result)
model <- lm(job_satisfaction~ freewill * age_group, data = wvs_data_usa)
summary(model)

# inferential statistics sex and freewill
t.test(freewill ~ Sex, data = wvs_data_usa )

lm_interaction <- lm(job_satisfaction ~ freewill * factor(Sex), data = wvs_data_usa)
summary(lm_interaction)
```
Interestingly, there are virtually no differences in the average belief in free will between the different age groups surveyed (@fig-ageboxplotwvs in @sec-apx-box). ANOVA confirmed that there are no significant differences (*F*(4,12809) = 1.032, *p* = 0.358). Age did also not influence the relationship between free will beliefs and job satisfaction (lowest *p* = 0.293). 
However, there is a significant difference of Sex on free will beliefs (@fig-sexboxplotwvs in @sec-apx-box), with women on average having marginally higher ratings (7.69) than men (7.61) (*p* < 0.05). We could not observe any significant effect of Sex on the relationship between free will beliefs and job satisfaction (*p* = 0.40).

## Comparison to Amazon Mechanical Turk Sample
```{r}
# Normalize free will scores between the two samples
satisfaction_data_usa_rel_num$freewill_norm <- (satisfaction_data_usa_rel_num$`Belief in Free Will (T1)` - 1)/(6-1)

wvs_data_usa$freewill_norm <- (wvs_data_usa$freewill - 1)/(10-1)

freewill_norm_mean_turk <- mean(satisfaction_data_usa_rel_num$freewill_norm, na.rm = TRUE)

freewill_norm_mean_wvs <- mean(wvs_data_usa$freewill_norm, na.rm = TRUE)

@@

## Demographic Boxplots for World Values Survey {#sec-apx-box}
```{r}
#| echo: false
#| warning: false
#| message: false
#| label: fig-ageboxplotwvs
#| fig-cap: "Belief in Free Will by Age Group in WVS 1981-2022"
